Packaging research artifacts with RO-Crate

### 2021-05-04 latex/ro-crate.tex
More figures from powerpoint

% From https://www.overleaf.com/latex/templates/using-the-stix2-opentype-fonts-with-lualatex-or-xelatex/hdfvhzqmhnpx
\usepackage{amsmath}
% \usepackage{hyperref}
\usepackage{fontspec}
% \usepackage{unicode-math}
% \usepackage{graphicx}

@@

% Welcome to the 2000s with UNICODE fonts!
% Adapted from
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting:_An_introduction_to_the_STIX2_OpenType_fonts
\setmathfont{STIX2Math}[
    Extension={.otf},
    Path=./STIX2fonts/,
    Scale=1
]
\setmainfont{STIX2Text}[
    Extension={.otf},
    Path=./STIX2fonts/,
    UprightFont={*-Regular},
    BoldFont={*-Bold},
    ItalicFont={*-Italic},
    BoldItalicFont={*-BoldItalic}
]
% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
    Extension={.otf},
    Path=./ttf-iosevka-slab-6.1.3/,
    Scale=MatchLowercase,
    UprightFont={*-thin},
    ItalicFont={*-lightitalic}
]

>>>>

% From https://www.overleaf.com/latex/templates/using-the-stix2-opentype-fonts-with-lualatex-or-xelatex/hdfvhzqmhnpx
\usepackage{amsmath}
% \usepackage{hyperref}
\usepackage{fontspec}
\usepackage{unicode-math}
% \usepackage{graphicx}

@@

% Welcome to the 2000s with UNICODE fonts!
% Adapted from
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting:_An_introduction_to_the_STIX2_OpenType_fonts
\setmathfont{STIX2Math}[
    Extension={.otf},
    Path=./STIX2fonts/,
    Scale=1
]
\setmainfont{STIX2Text}[
    Extension={.otf},
    Path=./STIX2fonts/,
    UprightFont={*-Regular},
    BoldFont={*-Bold},
    ItalicFont={*-Italic},
    BoldItalicFont={*-BoldItalic}
]
% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
    Extension={.ttf},
    Path=./ttf-iosevka-slab-6.1.3/,
    Scale=MatchLowercase,
    UprightFont={*-light},
    ItalicFont={*-lightitalic}
]
